---
title: "protViz Package for R"
author: Enes Kemal Ergin
output: github_document
date: January 19, 2018
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## About the package

protViz is an R package for visualizations, analysis of mass spectrometry data coming from proteomics experiments. 

### Trellis Plots 

Trellis graphs/plots (simply Trellis) are special plotting to graph multivariate data as an array of MxN panels. 

When the data includes a column of categorical data, or multiple columns characterizing some sort of nested sub-grouping of data, you might gain from plotting the data asa Trellis. [1](https://www.originlab.com/doc/Origin-Help/Trellis-Plot)


In the following 3 examples, we will look at the data they provided from Grossman et al 2010, J Proteomics[2], called ```fetuinLFQ```. Contains the subset of the data they used. 

```{r call some packages}
library(lattice)
library(protViz)
library(tidyr)
library(dplyr)
library(ggplot2)
```

```{r Look at the data provided for tutorial}
data(fetuinLFQ)
class(fetuinLFQ)
```

```{r print the main methods in list of dfs}
str(fetuinLFQ)
```

It seems like the dataset has 3 dataframes stored in a list, and seperated by method used to calculate the abundance; ```T3PQ, APEX, emPAI```. Each method-dataframe has 4 columns;

- ```conc```: concentration of the sample
- ```prot```: protein name or ID
- ```abundance```: Abundance value
- ```method```: Method used to calculate the abundance


 
```{r example1: calls APEX dataframe }
cv<-1-1:7/10
t<-trellis.par.get("strip.background")
t$col<-(rgb(cv,cv,cv))
trellis.par.set("strip.background",t)

my.xlab="Fetuin concentration spiked into experiment [fmol]"
my.ylab<-"Abundance"

xyplot(abundance~conc|prot*method, 
    data=fetuinLFQ$apex, 
    groups=prot,
    aspect=1,
    panel = function(x, y, subscripts, groups) {
        if (groups[subscripts][1] == "Fetuin")  {
            panel.fill(col="#ffcccc")
        }
                panel.grid(h=-1,v=-1)
                panel.xyplot(x, y)
                panel.loess(x,y, span=1)
            },
    xlab=my.xlab,
    ylab=my.ylab
)
```

__This plot could be used to show which proteins has more abundance in the dataset for Yeast, human, and both together.__ But overall, this is not exactly what I am looking for. 





## Resources

1. https://www.originlab.com/doc/Origin-Help/Trellis-Plot
2. Grossmann, J., Roschitzki, B., Panse, C., Fortes, C., Barkow-Oesterreicher, S., Rutishauser, D., & Schlapbach, R. (2010). Implementation and evaluation of relative and absolute quantification in shotgun proteomics with label-free methods. Journal of Proteomics, 73(9), 1740-1746. doi:10.1016/j.jprot.2010.05.011
3. 